### 2020-06-27 docs/LaTex/Paper.tex
Completes docs

Because of explained above, the gateway will just receive one package per each $\approx$10 minutes ---at line 74 in the sketch the transmission interval is set at 60 seconds, so as there are 9 channels but the gateway is just listening the channel 0, the microcontroller is transmitting at this channel once in 9---

@@

>>>>

Because of explained above, the gateway will just receive one package per each $\sim$10 minutes ---at line 74 in the sketch the transmission interval is set at 60 seconds, so as there are 9 channels but the gateway is just listening the channel 0, the microcontroller is transmitting at this channel once in 9---

@@

Once these steps are completed, the TTN web interface will provide an overview with all data regarding to the device like figure \ref{fig:dev_overview} shows.

\begin{figure}[ht]
  \centering
  \includegraphics[width=.9\textwidth]{../pictures/TTN_dev_overview.png}
  \caption{A device overview.}
  \label{fig:dev_overview}
\end{figure}

Another important consideration inside TTN platform is to check which decoder is chosen for the receives payloads, this can be check in
